Learning From Massive Noisy Labeled Data for Image Classification

### 2015-04-01 paper.tex
Add missing references

Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels. Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic}. Such methods may better avoid overfitting and utilize the relationships between the two datasets. However, we find that training a Convolutional Neural Network (CNN) from scratch with limited clean labels and massive noisy labels is better than finetuning only on the clean labels. Other approaches address the problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}. These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets. Therefore, it is inevitable to develop a better way of using huge amount of noisy labeled data.

@@

{\bf Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data. Label Propagation method \cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples. However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on largescale datasets. Weston et al. \cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features. But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.

{\bf Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features. However, the model parameters cannot be properly learned when training data is not enough. Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic}. Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related. In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.

@@

\subsection{Evaluation} % (fold)
\label{sub:evaluation}
The effectiveness of our model is validated based on a series of experiments. We exploit the AlexNet~\cite{krizhevsky2012imagenet} as our baseline model, which consists of five convolutional layers and three fully connected layers. Although recent models may have better learning capability, we choose AlexNet since it is well studied and much easier to be reimplemented (see the \texttt{bvlc\_reference\_caffenet}\footnote{\url{http://caffe.berkeleyvision.org/model_zoo.html}}).

>>>>

Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels. Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic,donahue2013decaf}. Such methods may better avoid overfitting and utilize the relationships between the two datasets. However, we find that training a Convolutional Neural Network (CNN) from scratch with limited clean labels and massive noisy labels is better than finetuning only on the clean labels. Other approaches address the problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}. These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets. Therefore, it is inevitable to develop a better way of using huge amount of noisy labeled data.

@@

{\bf Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data. Label Propagation method \cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples. However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on large-scale datasets. Chen \etal~\cite{chen2013fast} tackled this problem in the scenario of image tagging by a co-regularized duo classifier that can efficiently use both the image and incomplete tags. Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features. But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.

{\bf Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features. However, the model parameters cannot be properly learned when training data is not enough. Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}. Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related. In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.

@@

\subsection{Evaluation} % (fold)
\label{sub:evaluation}
The effectiveness of our model is validated based on a series of experiments. We implement our method by using Caffe~\cite{jia2014caffe} and exploit the AlexNet~\cite{krizhevsky2012imagenet} as the baseline model, which consists of five convolutional layers and three fully connected layers. Although recent models may have better learning capability, we choose AlexNet since it is well studied and much easier to be reimplemented (see the \texttt{bvlc\_reference\_caffenet}\footnote{\url{http://caffe.berkeleyvision.org/model_zoo.html}}).
